General Relativistic Ray Tracing for Neutrinos

### 2016-10-12 paper.tex
Write paper outline and add empty sections

@@

\section{Ray tracing formulation}

The neutrino distribution function, $f(p_\beta; x^\alpha)$ is an invariant
quantity counting the number of neutrinos in a given momentum volume centered on
$p_\beta$ and spatial volume centered on $x^\alpha$.
The neutrino momentum is written
\begin{equation}
  \label{eqn:def_momentum}
  p_\beta = \varepsilon (u_\beta + \ell_\beta),
\end{equation}
with $u^\beta$ a general observer's velocity,
$\varepsilon=-p_\mu u^\mu$ the energy measured by that observer,
and $\ell_\beta$ the direction vector subject to the constraints
$u^\alpha \ell_\alpha = 0$ and
$\ell^\alpha \ell_\alpha=1$.
Because $\ell$ is normalized and perpendicular to the observer's velocity,
it has two degrees of freedom, which we can make explicit by defining its
spatial components with respect to spherical polar angles
\begin{equation}
  \label{eq:def_direction}
  \ell_\alpha :=
  q (s,\sin\upsilon_1\cos\upsilon_2,\sin\upsilon_1\sin\upsilon_2,\cos\upsilon_1),
\end{equation}
with $q$ and $s$ functions of $\upsilon_1$ and $\upsilon_2$.

@@

\section{Fundamental Tests}

\section{Emission Spectra}
The high disk mass model is described in \cite{deat2013-leakage}.

\section{Closure Relation}

@@

\section{Source Terms}
\label{sec:source_terms}
The source terms comprising the right hand side of the Boltzmann Equation
(Eqn.~\ref{eqn:boltzmann}), can be analyzed in terms of the microphysical
processes of absorption/emission, elastic scattering, inellastic scattering,
and pair annihilation/production.

>>>>

\section{Introduction}

\subsection{What physics problems do we want to address?}

\subsection{Why ray tracing?}

\subsection{What is new/better about this ray tracing formulation?}

\subsection{Why does scattering matter?}

\subsection{In what ways is this method limited?}

\subsection{Outline}

In Sec.~\ref{sec:formulation} we derive the ray tracing equations from the
Boltzmann equation and describe our numerical scheme.
In Sec.~\ref{sec:tests} we present some tests of the code.
In Sec.~\ref{sec:applications} we present two applications:
neutrino spectra as a function of observer's angle, and
a variable closure relation for a truncated moment formalism.
We present both applications in the dynamical environments following the merger
of a neutron star--neutron star and a black hole--neutron star binary.

@@

\section{Ray tracing formulation}
\label{sec:formulation}

The neutrino distribution function, $f(x^\alpha; p_\beta)$ is an invariant
quantity counting the number of neutrinos in a given momentum volume centered on
$p_\beta$ and spatial volume centered on $x^\alpha$.
We may decompose the neutrino momentum
\begin{equation}
  \label{eqn:def_momentum}
  p_\beta = \varepsilon (u_\beta + \ell_\beta),
\end{equation}
with $u^\beta$ some fiducial observer's velocity,
$\varepsilon=-p_\mu u^\mu$ the energy measured by that observer,
and $\ell_\beta$ the direction subject to the constraints
$u^\alpha \ell_\alpha = 0$ and
$\ell^\alpha \ell_\alpha=1$.
With this decompositon we can write the arguments to the distribution function
$f(x^\alpha;\varepsilon,\ell_\beta)$.
Because $\ell_\beta$ is normalized and perpendicular to the observer's velocity,
it has two degrees of freedom, which we can make explicit by defining its
spatial components with respect to spherical polar angles
\begin{equation}
  \label{eq:def_direction}
  \ell_\alpha :=
  q (s,\sin\upsilon_1\cos\upsilon_2,\sin\upsilon_1\sin\upsilon_2,\cos\upsilon_1),
\end{equation}
with $q$ and $s$ functions of $\upsilon_1$ and $\upsilon_2$.

@@

\subsection{Numerical Implementation}
\label{sec:numerical}

\section{Fundamental Tests}
\label{sec:tests}

\section{Applications}
\label{sec:applications}

\subsection{Emission Spectra}
\label{ssec:spectra}

The high disk mass model is described in \cite{deat2013-leakage}.

\subsection{Closure Relation}
\label{ssec:closure}

@@

\section{Source Terms}
\label{sec:source_terms}
Here we present the source terms comprising the right hand side of the
Boltzmann Equation (Eqn.~\ref{eqn:boltzmann}) in terms of the microphysical
processes of absorption/emission, elastic scattering, inellastic scattering,
and pair annihilation/production.
